---
title: "simulation"
author: "Amy Yeung"
date: "2022-11-03"
output: github_document
---


wow you can type multiple rows of text at the same time with shift+option!!
wow you can type multiple rows of text at the same time with shift+option!!
wow you can type multiple rows of text at the same time with shift+option!!
wow you can type multiple rows of text at the same time with shift+option!!
wow you can type multiple rows of text at the same time with shift+option!!


```{r}
library(tidyverse)
```


## Simulations!!

```{r}
sim_mean_sd = function(n_obs, mu = 7, sigma = 4) {
   x = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(
  mu_hat = mean(x),
  sigma_hat = sd(x)
  )
}
```


How did we use this before?

```{r}
sim_mean_sd(n_obs = 30)
sim_mean_sd(n_obs = 30)
sim_mean_sd(n_obs = 30)

```


Each time returns a different result - How do we put them all together?

Let's start with a for loop!

```{r}
output = vector("list", length = 100) # do it 100 times

for (i in 1:100) {
  output[[i]] = sim_mean_sd(n_obs = 30)
}

bind_rows(output) 
```

Let's use list columns instead

`expand_grid` to give all possible combinations of inputs

```{r}
sim_results_df =
expand_grid(
  sample_size = 30,
  iteration = 1:100
) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) +
  geom_density()
```


!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

## What about changing the sample size?

```{r}
sim_results_df =
  expand_grid(
  sample_size = c(30, 60, 90, 120),
  iteration = 1:100
) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

4 sample sizes, 100 replicates each time - can look at distribution of sample means and sd.

```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) +
  geom_violin()
```

```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  group_by(sample_size) %>% 
  summarise(
    emp_st_err = sd(mu_hat)
  )
```

Let's see 2 inputs with `map2`

```{r, cache=TRUE}
sim_results_df =
  expand_grid(
  sample_size = c(30, 60, 90, 120),
  true_sigma = c(6, 3),
  iteration = 1:1000
) %>% 
  mutate(
    estimate_df = map2(.x = sample_size, .y = true_sigma, ~sim_mean_sd(n_obs = .x, sigma = .y)) 
  ) %>% 
  unnest(estimate_df)
```


```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) +
  geom_violin() +
  facet_grid(.~ true_sigma)
```

Knitting simulations takes some time; start with small sample sizes and make sure things knit first, then increase sample size.



